---
title: "Time Series forecasting with mlr3"
author: "Cornelia Gruber"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Time Series forecasting with mlr3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load}
library(data.table)
library(mlr3temporal)
library(mlr3)
library(ggplot2)
library(forecast)
library(anytime)
``` 

## Load and prepare data

In this vignette we are going to use the example of forecasting atmospheric data from Munich (muc) and New York City (nyc). 
We are interesting in forecasting three quantities: `"TAVG", "TMIN", "TMAX"`, the average, minimum and maximum temperature on a given day.

We first obtain the data from the **NOAA** (National Centers for Environmental Information, National Oceanic and Atmospheric Administration) website.

```{r data}
# Download the data
muc = read.csv("https://www.ncei.noaa.gov/data/global-summary-of-the-year/access/GM000004199.csv")
nyc = read.csv("https://www.ncei.noaa.gov/data/global-summary-of-the-year/access/USW00094728.csv")

# And subset columns
columns = c("DATE", "PRCP", "TAVG", "TMIN", "TMAX")
muc = muc[, columns]
nyc = nyc[, columns]
```

The data contains few missing values and years.
We will have to deal with them before forecasting.

```{r missing}
# Add missing years.
fill_missing = function(data, date) {
  # Filter all-na rows
  data = data[!apply(data, 1, function(x) {all(is.na(x))}), ]
  # Add all missing dates from start to end of time-series
  dates = data[[date]]
  missing = setdiff(seq(from = min(dates, na.rm = TRUE), to = max(dates, na.rm = TRUE)), dates)
  if (length(missing)) {
    dt_miss = data.table(DATE = missing, PRCP = NA, TAVG = NA, TMIN = NA, TMAX = NA)
    data = rbind(data, dt_miss)
  }
  data[[date]] = as.POSIXct(as.character(data[["DATE"]]), format = "%Y")
  return(data.table(data[order(data[[date]]),]))
}

muc = fill_missing(muc, "DATE")
nyc = fill_missing(nyc, "DATE")
```

## Generate Task

We can now supply this `data.table` to create a new `TaskRegrForecast`.

```{r task}
task = TaskRegrForecast$new(
  id = "nyc",
  backend = nyc,
  target = c("TAVG", "TMIN", "TMAX"),
  date_col = "DATE"
)
task$print()
```

## Learner

```{r learner}
learner = LearnerRegrForecastVAR$new()
learner$train(task, row_ids = 1:140)
learner$model
```


## Predict

```{r predict}
p = learner$predict(task, row_ids = 141:150)

p$response
```

## Rolling Window CV

```{r rollingwindow}

rr = rsmp("RollingWindowCV", fixed_window = F)
rr$instantiate(task)
resample = resample(task, learner, rr, store_models = TRUE)

resample$predictions()[1:2]
```

## Plotting

```{r plot}

autoplot(task) + ggtitle("NYC - Yearly Climate Data")

task = TaskRegrForecast$new(
  id = "muc",
  backend = ts_dt(muc),
  target = "TAVG",
  date_col = "DATE"
)

autoplot(task) + ggtitle("MUC - Yearly Climate Data")

learner = LearnerRegrForecastAutoArima$new()
learner$train(task, row_ids = 1:85)
learner$model
p = learner$predict(task, row_ids = 86:136)
p$se


checkresiduals(learner$model)

autoplot(forecast(learner$model, xreg = as.matrix(task$data(cols = "PRCP", rows = 131:136)))) + ylab("value")
```
